\textbf{Course: Física Teórica I (CDP7600)} \\[0.2cm] {\Large \textbf{Project}: \hspace{0.2cm} \textit{Fibration building blocks of information-processing networks} }

### 2019-11-04 Manuscript/main.tex
Finishing manuscript

Fibration building blocks of information-processing networks represent the sets of nodes that are symmetrical with respect to the processing of input signals received from the rest of the network, defining this way the classes of nodes that process equivalent information. In this report, I reproduced relevant results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real systems data. More specifically, using the transcriptional regulatory network data from the \textit{Escherichia Coli} bacteria, I quantify the clusters of nodes in the network that synchronously process equivalent information, and then I classify these clusters, called fibers, based on its specific topological features. Here, to consistently present the obtained results, I briefly introduce the theory concerning the graph fibration morphism and its main definitions related to information processing symmetries. Then, I detail the computational methods adopted to the identification of the network fibers, presenting a slightly different algorithmic approach for the problem in hand, based on the general relational refinement partitioning algorithms described by Paige and Tarjan in 1987. After defining the implementation details of the graph refinement algorithm I lastly apply the method for trial network examples and then for the constructed genetic regulatory network of \textit{Escherichia Coli}, noticing a visible discrepancy between the results obtained by the methods described in this report and the results exhibited in the most recent literature given at \textit{Morone et. al.} (2019). The results showed in this report, concerning the fibers distribution over the network, are tested and verified to support the assertion that the algorithm used captures the correct minimal fibration.

>>>>

Fibration building blocks of information-processing networks represent the sets of nodes that are symmetrical with respect to the processing of input signals received from the rest of the network, defining this way the classes of nodes that process equivalent information. In this report, I reproduced relevant results concerning the identification and classification of the fibration building blocks of directed networks, constructed from real systems data. More specifically, using the transcriptional regulatory network data from the \textit{Escherichia Coli} bacteria, I quantify the clusters of nodes in the network that synchronously process equivalent information, and then I classify these clusters, called fibers, based on its specific topological features. Here, to present the obtained results, I briefly introduce the theory concerning the graph fibration morphism and its main definitions related to information processing symmetries. Then, I detail the computational methods adopted to the identification of the network fibers, presenting the algorithmic approach for the problem in hand, based on the general relational refinement partitioning algorithms described by Paige and Tarjan in 1987. After defining the implementation details of the graph refinement algorithm I apply the method for trial network examples and then for the constructed genetic regulatory network of \textit{Escherichia Coli}, noticing the equivalence between the results obtained by the methods described in this report and the results exhibited in the most recent literature given at \textit{Morone et. al.} (2019). The results showed in this report, concerning the fibers distribution over the network, are tested and verified to support the assertion that the algorithm used captures the correct minimal fibration.
